The markings of the trade: exploring the patterns of olive oil production in Roman Baetica

### 2018-06-04 Paper/jaccardbaetica.tex
review

The distribution of amphora stamps in different conventus can be seen in Fig. \ref{frequency}. The majority of stamps found are concentrated in \textit{Hispalis} with 574 stamps while \textit{Corduba} and \textit{Astigi} with 267 and 146 stamps, respectively. Mostly workshops show a homogeneity on frequency of stamps except La Catria and Arva (both show 29 different stamps) that show a big amount of different stamps. According to some researchers, those workshops became in one of the most important centres of amphora production although it could have been more intensely prospected then others. \citep{arva_1997}

>>>>

The distribution of amphora stamps in different conventus can be seen in Fig. \ref{frequency}. The majority of stamps found are concentrated in \textit{Hispalis} with 574 stamps while \textit{Corduba} and \textit{Astigi} with 267 and 146 stamps, respectively. Mostly workshops show a homogeneity on frequency of stamps except La Catria and Arva (both show 29 different stamps) that show a big amount of different stamps. According to some researchers, those workshops became in most important centres of amphora production although it could have been more intensely prospected then others. \citep{arva_1997}
